sem

### 2023-02-14 scripts/workshop/sem.Rmd
latent variable modeling

```{r, message = F}
library(here)
library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(mgcv)
library(dagitty)
```

@@

>>>>

```{r, message = F}
library(here)
library(tidyverse)
library(magrittr)
library(piecewiseSEM)
library(nlme)
library(lmerTest)
library(mgcv)
library(dagitty)
library(lavaan)
```

@@

# Latent Variable Modeling using lavaan

```{r}
potential <- comm_data %>% mutate(log_cc = log10(cc), log_size = log10(size)) %>% select(cc, log_cc, size, log_size, MeanWaterTempPredC, Prevalence) %>% drop_na() %>% filter(MeanWaterTempPredC > 0)
cor(potential[,c(2,4,5)])
```

```{r}
potential_formula <- "potential =~ log_cc + log_size + MeanWaterTempPredC"
potential_model <- sem(potential_formula, potential)
```

```{r}
summary(potential_model)
```

```{r}
potential_formula_1 <- "
potential =~ log_cc + log_size + MeanWaterTempPredC

Prevalence ~ potential
"

potential_model_1 <- sem(potential_formula_1, potential)
```

```{r}
summary(potential_model_1)
```
